\section{Conference and Workshop Publications}

\cvitem{}{\textbf{Mark Wilkening}, Udit Gupta, Samuel Hsia, Caroline Trippel, Carole-Jean Wu, David Brooks, and Gu-Yeon Wei. 2021. \textit{RecSSD: Near Data Processing for Solid State Drive Based Recommendation Inference.} In Proceedings of the 26th ACM International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS 2021). Association for Computing Machinery, New York, NY, USA, 717–729. DOI:https://doi.org/10.1145/3445814.3446763}
\cvitem{}{Udit Gupta, Samuel Hsia, Jeff Zhang, \textbf{Mark Wilkening}, Javin Pombra, Hsien-Hsin Sean Lee, Gu-Yeon Wei, Carole-Jean Wu, and David Brooks. 2021. \textit{RecPipe: Co-designing Models and Hardware to Jointly Optimize Recommendation Quality and Performance.} In MICRO-54: 54th Annual IEEE/ACM International Symposium on Microarchitecture (MICRO '21). Association for Computing Machinery, New York, NY, USA, 870–884. DOI:https://doi.org/10.1145/3466752.3480127}
\cvitem{}{S. Hsia, U. Gupta, \textbf{M. Wilkening}, C. -J. Wu, G. -Y. Wei and D. Brooks, \textit{"Cross-Stack Workload Characterization of Deep Recommendation Systems,"} 2020 IEEE International Symposium on Workload Characterization (IISWC), 2020, pp. 157-168, doi: 10.1109/IISWC50251.2020.00024.}
\cvitem{}{\textbf{M. Wilkening}, F. Previlon, D. R. Kaeli, S. Gurumurthi, S. Raasch and V. Sridharan, \textit{"Evaluating the Resilience of Parallel Applications,"} 2018 IEEE International Symposium on Defect and Fault Tolerance in VLSI and Nanotechnology Systems (DFT), 2018, pp. 1-6, doi: 10.1109/DFT.2018.8602987.}
\cvitem{}{F. Previlon, \textbf{M. Wilkening}, V. Sridharan, S. Gurumurthi, and D. Kaeli. \textit{"Examining the Impact of ACE interference on Multi-Bit AVF Estimates"}. In Workshop on System Effects of Logic Soft Errors (SELSE-11), Austin, TX, April 2015.}
\cvitem{}{\textbf{M. Wilkening}, V. Sridharan, D. Kaeli, S. Gurumurthi, F. Previlon, and S. Li. \textit{"Calculating Architectural Vulnerability Factors for Spatial Multi-Bit Transient Faults"}. In International Symposium on Microarchitecture (MICRO-47), Cambridge, UK, December 2014.}
\cvitem{}{H. Jeon, \textbf{M. Wilkening}, V. Sridharan, S. Gurumurthi, and G. Loh. \textit{"Architectural Vulnerability Modeling and Analysis of Integrated Graphics Processors"}. In Workshop on System Effects of Logic Soft Errors (SELSE-9), Stanford, CA, March 2013.}

\section{Technical Articles and Presentations}

\cvitem{}{\textbf{Mark Wilkening}. \textit{"Infrastructure for AVF Modeling"}.
gem5 User Workshop at International Symposium of Computer Architecture (ISCA-42), Portland, OR, June 2015.}

\cvitem{}{Vilas Sridharan, \textbf{Mark Wilkening}, and Sudhanva Gurumurthi, \textit{"Determining the vulnerability of multi-threaded program code to soft errors"}. United States Patent, US 9292418 B2. Published March 22, 2016}
